%Archery by Carl Phillips - https://www.poetryfoundation.org/poetrymagazine/poems/153792/archery-5ed6f65e9da61
\section[Archery]{Archery || \emph{Carl Phillips} \hspace*{\fill}  \thepage}
\label{sec:Archery}
\vspace*{1.5cm}
\begin{Parallel}{0.48\textwidth}{0.48\textwidth}
\ParallelLText{\noindent
\-\ \indent \indent was still a thing, then. To have timed your arrow \\
a perfectly meant watching the air for a moment \\
seem stitched throughout with a kind of \\
timelessness. To have straddled at last, correctly, \\
the storm of falling in love (and staying there) meant \\
the smell of apples, victory, tangerines, and smoke \\
all mixed together on the breath 

\-\ \\of a stranger, half asleep still, just beginning to remember a bit, \\
as he stirs beside you. I dreamed we were young again, \\
he’s mumbling, as if to someone whose name he’s known \\
long enough to have called it out more than once in anger \\
and sex and fear equally. Somewhere happiness too, 

\-\ \\right? All those hours spent trying to outstare the distance\\
of what the days must come to, } 

\ParallelRText{\noindent
and pretending a choice to it: now the shadow-script\\
that willows and hazel trees mark the barn’s western\\
face with; now the wind-rippled field, like a lesser version—tamer,\\
tameable—of the sea, for movement (same infinite\\
pattern, and variation; randomness and intention; release;\\
restraint—that kind of movement) ...

\-\ \\ \indent \indent \indent \indent \indent \indent \indent \indent \indent \indent \indent Dear saddle\\
of gentleness. Dear moss, sweet moss that only\\
the dark and wet and patience make possible. To sing a song\\
of water, and not drown in it. And some calling that\\
a good trick. And some calling it

\-\ \\mastery. That last flickering before nightfall. From beneath\\
the low branches. I dreamed we were new again. Stars. Just a little\\
past dusk.}
\ParallelPar
\end{Parallel}