%%Say Thank You Say I’m Sorry by Jericho Brown - https://www.nytimes.com/2020/06/15/books/review/jericho-brown-say-thank-you-say-im-sorry-poem-coronavirus.html

\section[Say Thank You Say I’m Sorry ]{Say Thank You Say I’m Sorry || \emph{Jericho Brown} \hspace*{\fill}  \thepage}
\vspace*{2cm}
\begin{Parallel}{0.48\textwidth}{0.48\textwidth}
\ParallelLText{\noindent
I don’t know whose side you’re on,\\
But I am here for the people\\
Who work in grocery stores that glow in the morning\\
And close down for deep cleaning at night\\
Right up the street and in cities I mispronounce,\\
In towns too tiny for my big black\\
Car to quit, and in every wide corner\\
Of Kansas where going to school means\\
At least one field trip\\
To a slaughterhouse. I want so little: another leather bound\\
Book, a gimlet with a lavender gin, bread\\
So good when I taste it I can tell you\\
How it’s made. I’d like us to rethink\\
What it is to be a nation. I’m in a mood about America\\
Today. I have PTSD\\
About the Lord. God save the people who work}
\ParallelRText{\noindent
In grocery stores. They know a bit of glamour\\
Is a lot of glamour. They know how much\\
It costs for the eldest of us to eat. Save\\
My loves and not my sentences. Before I see them,\\
I draw a mole near my left dimple,\\
Add flair to the smile they can’t see\\
Behind my mask. I grin or lie or maybe\\
I wear the mouth of a beast. I eat wild animals\\
While some of us grow up knowing\\
What gnocchi is. The people who work at the grocery don’t care.\\
They say, \emph{Thank you}. They say, \emph{Sorry},\\
\emph{We don’t sell motor oil anymore} with a grief so thick\\
You could touch it. Go on. Touch it.\\
It is early. It is late. They have washed their hands.\\
They have washed their hands for you.\\
And they take the bus home.}
\ParallelPar
\end{Parallel} 