%My mother texts me instructions to cook silken tofu by Sue Zhao - https://www.reddit.com/r/Poetry/comments/oml6w4/poem_my_mother_texts_me_instructions_to_cook/
\section[My mother texts me instructions to cook silken tofu]{My mother texts me instructions to cook silken tofu || \emph{Sue Zhao} \hspace*{\fill}  \thepage}
\vspace*{1.7cm}
\begin{Parallel}{0.48\textwidth}{0.48\textwidth}
\ParallelLText{\noindent
\emph{Do you have white pepper?} She asks. \emph{Spring}\\
\emph{onions? Corn starch?} No. Yes, a sprig. No.\\
\emph{Do you have sesame oil?}\\
\-\ \\\emph{First, you must sauté some prawns,} she says. \\
\emph{It will compliment the texture of the tofu.} I don't \\
have prawns, I say, will bacon do? She pauses.\\
\-\ \\\emph{Maybe it is easier if I give you a call.}\\
\-\ \\\emph{Cut it into cubes and put it into the pot,} her voice\\
rings through the phone. \emph{How was your day?}\\
\-\ \\It was fine. How big should I make them?\\
\-\ \\\emph{You know I'm proud of you? she says.}\\
\-\ \\For what? I laugh. I can't even make tofu.\\}
\ParallelRText{\noindent
\emph{For trying,} she says. \emph{For not giving up. You can\\
cut them roughly -\\
just don't make them too small.}\\
\-\ \\In my mother is a dream unfulfilled. Perhaps\\
that is true of most mothers.\\
In her is an outpouring of love. I want to\\
give her something so I try to be good.\\
\-\ \\It is 10pm when we say goodnight. Thank you \\
for the recipe I say - I mean, \\
thank you for raising me. \emph{Don't forget to} \\
\emph{wash your dishes,} she replies.\\
\-\ \\Sometimes life is simple, I think. I am happy.\\
\-\ \\I have a mother.\\
\-\ \\She calls me and teaches me how to cook tofu.}
\ParallelPar
\end{Parallel}